QPLIB: A Library of Quadratic Programming Instances

### 2016-09-08 QPLIB-1.0.tex
Add a table of applications

On the other hand, (MI)QP is, in some sense, a considerably more expressive class than (MI)LP. Quadratic expressions are found, either naturally or after appropriate reformulations, in very many practical problems (\cite{Kochenberger2014}, {\bf citations?}). In general, any continuous function can be approximated with arbitrary accuracy (over a compact set) by a polynomial of arbitrary degree; in turn, every polynomial can be broken down to a system of quadratic expressions. Hence, (MI)QP is, in some sense, roughly as expressive as the whole of (MI)NLP. Of course this is, in principle, true for (MI)LP as well, but at the cost of much larger and much more complex formulations ({\bf citations?}). Hence, for many applications QP may represent the ``sweet spot'' between the effectiveness, but lower expressive power, of (MI)LP and the higher expressive power, but much higher computational cost, of (MI)NLP.

\ldots

>>>>

On the other hand, (MI)QP is, in some sense, a considerably more expressive class than (MI)LP. Quadratic expressions are found, either naturally or after appropriate reformulations, in very many practical problems \cite{Kochenberger2014}. We survey several of these applications in Table \ref{tbl:application}. In general, any continuous function can be approximated with arbitrary accuracy (over a compact set) by a polynomial of arbitrary degree; in turn, every polynomial can be broken down to a system of quadratic expressions. Hence, (MI)QP is, in some sense, roughly as expressive as the whole of (MI)NLP. Of course this is, in principle, true for (MI)LP as well, but at the cost of much larger and much more complex formulations ({\bf citations?}). Hence, for many applications QP may represent the ``sweet spot'' between the effectiveness, but lower expressive power, of (MI)LP and the higher expressive power, but much higher computational cost, of (MI)NLP.

\begin{center}
\begin{longtable}{ lcl }
%
\caption{Application Domains of (MI)QP}\label{tbl:application} \\
%
\toprule
Problem & Discrete? & Contributions \\
\midrule
\endfirsthead
%
\multicolumn{3}{l}{\emph{Table \ref{tbl:application} (Application Domains of (MI)QP) continued}} \\
\toprule
Problem & Discrete? & Contributions \\
\midrule
\endhead
%
\midrule 
\multicolumn{3}{l}{\multirow{1}{\textwidth}{$^{\ddagger}$Applications with many manuscripts cite reviews and recent works \\[-12pt] \phantom{hi} \hfill \emph{continued}}} \\ \\
\endfoot
%
\bottomrule 
\multicolumn{3}{l}{\multirow{1}{\textwidth}{$^{\ddagger}$Applications with many manuscripts cite reviews and recent works. $^{\star}$TSP $\equiv$ Traveling Salesman Problem}} \\ \\ \\
\endlastfoot
%
\multicolumn{3}{l}{{\bf Classical Problems that can be formulated as MIQP}} \\[1pt]
%
\multirow{1}{.55\textwidth}{Quadratic Assignment Problem (QAP)$^{\ddagger}$} & \checkmark & \cite{anstreicher:2003,loiola-etal:2007} \\ \cmidrule(rl){2-3}
%
Max-Cut & \checkmark & \cite{Rendl2008} \\ \cmidrule(rl){2-3}
%
Maximum clique$^{\ddagger}$ & \checkmark & \cite{bomze-etal:1999} \\
\midrule
%
\multicolumn{3}{l}{{\bf Computational chemistry \& Molecular biology}} \\[1pt]
%
Zeolites && \cite{gounaris-etal:2013} \\
%
\midrule
%
\multicolumn{3}{l}{{\bf Computational geometry}} \\[1pt]
%
\multirow{1}{.55\textwidth}{Layout design} & \checkmark & \cite{anjos-liers:2012,castillo-etal:2005,dorneich-sahinidis:1995} \\ \cmidrule(rl){2-3}
%
\multirow{1}{.55\textwidth}{Maximizing polygon dimensions} && \cite{audet-etal:2011,audet-etal:2007,Audet-etal:2009,audet-etal:2002,Audet-Ninin:2013} \\ \cmidrule(rl){2-3}
%
Packing circles$^{\ddagger}$ && \cite{hifi-mhallah:2009,szabo-etal:2005} \\ \cmidrule(rl){2-3}
%
Nesting polygons && \cite{kallrath:2009,rebennack-etal:2009} \\ \cmidrule(rl){2-3}
%
Cutting ellipses && \cite{kallrath-rebennack:2013} \\ %\cmidrule(rl){2-3}
%Nonconvex shapes \\
\midrule
%
\multirow{1}{.55\textwidth}{{\bf Finance:} Portfolio selection optimization} && \multirow{1}{.25\textwidth}{\cite{deng-etal:2013,kallrath:2003,lin-etal:2005,maranas-etal:1997,parpas-rustem:2006,rios-sahinidis:2010}} \\ 
%
\midrule
%
\multicolumn{3}{l}{{\bf Process Networks}} \\[1pt]
%
%\multicolumn{3}{l}{Process networks optimisation problems typically involve two} \\
%
\multirow{1}{.55\textwidth}{Crude oil scheduling} & \checkmark & \cite{li-etal:2007,li-etal:2011,li-etal:2012,mouret-etal:2009,mouret-etal:2011} \\ \cmidrule(rl){2-3}
%
\multirow{1}{.55\textwidth}{Data reconciliation} & \checkmark & \cite{ruiz-grossmann:2011} \\ \cmidrule(rl){2-3}
%
\multirow{1}{.55\textwidth}{Multi-commodity flow} & \checkmark & \cite{tadayon-smith:2013} \\ \cmidrule(rl){2-3}
%
\multirow{1}{.55\textwidth}{Multi-period blending} & \checkmark & \cite{kolodziej-etal:2013:jogo,kolodziej-etal:2013} \\ \cmidrule(rl){2-3}
%
\multirow{1}{.55\textwidth}{Natural gas networks} & \checkmark & \cite{hasan-etal:2011,li-etal:2011-aiche_journal,li-etal:2011-jogo} \\ \cmidrule(rl){2-3}
%
Pooling$^{\ddagger}$ & \checkmark & \multirow{1}{.25\textwidth}{\cite{Alfaki-Haugland:2013,Castillo-etal:2013,dambrosio-etal:2011pooling,Faria-Bagajewicz:2012,misener-floudas:2009,misener-floudas:2010-genpooling,Papageorgiou-etal:2012,pham-etal:2009,ruiz-etal:2013,visweswaran:2009}} \\ \\ \cmidrule(rl){2-3}
%
\multirow{1}{.55\textwidth}{Open-pit mine scheduling} & \checkmark & \cite{bley-etal:2012} \\ \cmidrule(rl){2-3}
%
Reverse osmosis & \checkmark & \cite{saif-etal:2008} \\ \cmidrule(rl){2-3}
%
Supply chain & \checkmark & \cite{nyberg-etal:2012} \\ \cmidrule(rl){2-3}
%
Water networks$^{\ddagger}$ & \checkmark & \multirow{1}{.25\textwidth}{\cite{ahmetovic-grossmann:2010,bagajewicz:2000,bragalli-etal:2011,castro-teles:2013,geissler-etal:2013,gleixner-etal:2012,jezowski-2010,khor-etal:2014,ponceortega-etal:2010,teles-etal:2012}} \\ \\
%
\midrule
%
\multicolumn{3}{l}{{\bf Robotics}} \\[1pt]
%
\multirow{1}{.55\textwidth}{TSP$^{\star}$ with Neighborhoods} & \checkmark & \cite{gentilini-etal:2013} \\
%
\end{longtable}
\end{center}
